Deep Embedded Clustering for Open Cluster Characterization with Gaia DR2 Data

### 2021-03-09 paper/paper.tex

%---------------------------
%marges
%---------------------------
%\usepackage[margin=1.9cm]{geometry}
%---------------------------
%---------------------------
%---------------------------
%---------------------------

@@

%\renewcommand{\listfigurename}{Índice de Ilustraciones}
%\renewcommand{\listtablename}{Índice de Tablas}
%\renewcommand{\contentsname}{Índice de Contenidos}
%\renewcommand{\figurename}{Figura}
%\renewcommand{\tablename}{Tabla}
%\twocolumn

%\frontmatter
%\tableofcontents
%\listoffigures
%\listoftables

@@

Our DECOCC model was implemented in Python 3.8 using the Keras 2.2 framework and Jupyter
Notebooks~\cite{Kluyver2016jupyter}. All tests were run on an Apple Mac Pro Late 2013 with a
2.7GHz 12-Core Intel Xeon E5-2697v2, and 64GB RAM 1866MHz DDR3. For the GPU, we use a graphic
card AMD FirePro D700 with 6GB~\footnote{All resources developed for this project are available
at \href{https://github.com/cdalvaro/machine-learning-master-thesis}
{https://github.com/cdalvaro/machine-learning-master-thesis}}.

>>>>

@@

@@

Our DECOCC model was implemented in Python 3.8 using the Keras 2.2 framework and Jupyter Notebooks~\cite{Kluyver2016jupyter}. All tests were run on an Apple Mac Pro Late 2013 with a 2.7GHz 12-Core Intel Xeon E5-2697v2, and 64GB RAM 1866MHz DDR3. For the GPU, we use a graphic card AMD FirePro D700 with 6GB~\footnote{All resources developed for this project are available at \href{https://github.com/cdalvaro/machine-learning-master-thesis}{https://github.com/cdalvaro/machine-learning-master-thesis}}.
